%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Computer Engineering (Innovative Technologies, Embedded Systems)} % Degree
    {Scuola Superiore Sant'Anna} % Institution
    {Pisa, Italy} % Location
    {Nov. 2010 - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Quality of Service} control for soft real-time systems.}
	\item {Analysis, design and development of \textbf{multiprocessor real-time scheduling
		and synchronization} solutions.}
	\item {Design and development of \textbf{embedded and real-time systems}.}
	\item {Linux kernel \textbf{SCHED\_DEADLINE patchset maintainer} (real-time
		deadline scheduling) - merged in mainline since Linux 3.14.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Scholar} % Degree
    {University of California at Santa Cruz - Sytems Research Group} % Institution
    {Santa Cruz (CA), USA} % Location
    {Sep. 2012 - Mar. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {Design and development of \textbf{real-time scheduling
		mechanisms} for the \textbf{Linux kernel}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master's degree in Computer Engineering} % Degree
    {University of Pisa - Faculty of Computer Engineering} % Institution
    {Pisa, Italy} % Location
    {Mar. 2007 - Jun. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {Thesis: "Design and Development of Deadline Based Scheduling
		Mechanisms for Multiprocessor Systems".}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bachelor's degree in Computer Engineering} % Degree
    {University of Pisa - Faculty of Computer Engineering} % Institution
    {Pisa, Italy} % Location
    {Sep. 2002 - Jun. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {Thesis: "Concurrent C++ code generation from UML statecharts".}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Scientific High School degree} % Degree
    {``G. Marconi'' High School} % Institution
    {Grosseto, Italy} % Location
    {Sep. 1997 - Jul. 2002} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
	\item {General scientific preparation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
