%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {ARM Ltd.} % Organization
    {Cambridge, UK} % Location
    {Jul. 2014 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Operating system support for big.LITTLE and next-generation ARM technology.}
	\item {\textbf{Linux kernel} support and development for \textbf{scheduler and power management} frameworks.}
        \item {\textbf{Maintainer} of the \textbf{SCHED\_DEADLINE Linux scheduling class}.}
	\item {Workload \textbf{power and performance analysis} (kernel level) on \textbf{Linux/Android}.}
	\item {Collaborated with the \textbf{Google Android kernel team} for the
		release of the \textbf{Pixel Android phone}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Contributions within the EU Research Project “Java Platform for High-Performance
	and Real-Time Large Scale Data”} % Organization
    {Pisa, IT} % Location
    {Jan. 2013 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {JUNIPER - FP7-ICT-2011.4.4 - Grant Agreement No. 318763 - http://www.juniper-project.org/} % Organization
	\item {Development and maintenance of the SCHED\_DEADLINE scheduler for
		the Linux kernel.}
        \item {Implementation of the Multiprocessor Bandwidth Inheritance
		real-time synchronization protocol in Linux.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Contributions to the EU Research Project “Service Oriented Operating Systems”} % Organization
    {Pisa, IT} % Location
    {Feb. 2011 - Jul. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {SoOS - FP7-ICT-2009.8.1 - Grant Agreement No. 248465 - http://www.soos-project.eu/} % Organization
	\item {Contributions to deliverables: D3.4 “Protocols”, D4.4 “Execution Management”, D7.3.2
	       “Collaboration and Dissemination II”.}
       \item {Demo for 2\textsuperscript{nd} year project review.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Retis Lab (Scuola Superiore Sant'Anna of Pisa)} % Organization
    {Pisa, IT} % Location
    {Jan. 2011 - Apr. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {\textbf{Linux kernel} developer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Librarian} % Job title
    {Library of Veterinary Medicine (University of Pisa)} % Organization
    {Pisa, IT} % Location
    {Jun. 2009 - Nov. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Loan officer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tutor} % Job title
    {Faculty of Engineering (University of Pisa)} % Organization
    {Pisa, IT} % Location
    {Feb. 2009 - May 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Tutor of 1st year students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Linux/Windows Operating Systems Analyst/Administrator} % Job title
    {Faculty of Engineering (University of Pisa)} % Organization
    {Pisa, IT} % Location
    {Apr. 2007 - Jul. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Software/Hardware maintenance, systems configuration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Administrative staff assistant} % Job title
    {Admissions Office (University of Pisa)} % Organization
    {Pisa, IT} % Location
    {Nov. 2005 - Feb. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Filing clerk, students tutor.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
